Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-07 sections/01-introduction.tex
Update on Overleaf.

 While the introduction of new medical measurement methods requires a comprehensive evaluation and comparison with established standard measurement methods to ensure their validity and reliability, it is generally important for forecasts and nowcasting methods to assess the extent to which the predictions correspond to the development of reality. Conventionally, the methods are evaluated using distance measures that take aggregated local absolute differences between predictions (or measurements) and target values into account. For example, the Continuous Ranked Probability Score (CRPS) can be used to evaluate the accuracy of probabilistic predictions. It is also based on the integrated squared differences between the cumulative distribution function (CDF) of the prediction and the Heaviside jump function. These measures all fail to take sufficient account of whether the right direction of change is being taken, which can often be highly relevant in practice.

To detect the systematic difference between one measurement method with a gold standard method, a paired t-test can be performed on the pairwise difference of the two series of measurements to test the null hypothesis that the true mean difference is zero (\cite{watson2010method}). In addition, various indices such as the interclass correlation coefficient or Lin's concordance correlation, which were originally introduced as a modification of the Pearson correlation, have been proposed in practice to check the reproducibility of the measurement or to compare different measurement methods (\cite{lawrence1989concordance,koo2016guideline}). 
Furthermore, graphical tools were developed, such as the Bland-Altman diagram, which visualizing the differences between the methods in relation to their mean value (\cite{bland1986statistical}).

>>>>

 While the introduction of new medical measurement methods requires a comprehensive evaluation and comparison with established standard measurement methods to ensure their validity and reliability, it is generally important for forecasts and nowcasting methods to assess the extent to which the predictions correspond to the development of reality. Conventionally, the methods are evaluated using distance measures that take aggregated local absolute differences between predictions (or measurements) and target values into account. For example, the Continuous Ranked Probability Score (CRPS) can be used to evaluate the accuracy of probabilistic predictions. It is also based on the integrated squared differences between the cumulative distribution function (CDF) of the prediction and the Heaviside jump function. These measures all fail to take sufficient account of whether the right direction of change is being taken, which can often be highly relevant in practice. The information about whether an estimator (be it a measurement device, forecast or nowcas) can accurately predict the increase or decrease is important to determine whether a statement can be made about the direction of development of the actual value on the basis of the estimator's prediction results. In the following, we first provide an overview of the characteristics and evalutations of the three areas: Measurement, Prediction and Nowcasting and their relationship with Trending.

Measurement aims to obtain accurate and reliable data about the current state of a system. Often a certain parameter or variable is measured at regular intervals over a certain period of time. To detect the systematic difference between one measurement method with a gold standard method, a paired t-test can be performed on the pairwise difference of the two series of measurements to test the null hypothesis that the true mean difference is zero (\cite{watson2010method}). In addition, various indices such as the interclass correlation coefficient or Lin's concordance correlation, which were originally introduced as a modification of the Pearson correlation, have been proposed in practice to check the reproducibility of the measurement or to compare different measurement methods (\cite{lawrence1989concordance,koo2016guideline}). 
Furthermore, graphical tools were developed, such as the Bland-Altman diagram, which visualizing the differences between the methods in relation to their mean value (\cite{bland1986statistical}).
